---
title: "Final Project"
author: "YU FAN"
date: "2020/3/10"
output: html_document
---

```{r}
knitr::opts_chunk$set(echo = FALSE, 
                      comment = NA, # Recommended
                      fig.path = "./figures/",  # Store all figures here in relative path (make the folder first)
                      fig.align = "center",
                      fig.width = 7,
                      fig.height = 7,
                      message = FALSE, # Turn off load messages
                      warning = FALSE # Turn off warnings
                      )

```



## Introduction
In this project, we try to analysis the evolution of COVID-19 in the whole world. We use two dataset in our project, the first one is breakdown of cases and deaths of COVID-19 by country in the <https://www.worldometers.info/coronavirus/>. And the second data is come from <https://worldpopulationreview.com/countries/> which contains the world population data of each country.

In the following part, we first try to visuliza the death rate(total death/population) Prevalence rate (total COVID-19 case/population)and of each country in the world by the leaflet map. Then we try to analyze the realtionship of total death with the other factors. The factors contain total case number, total recover number,SeriousCritical number, active case number, total test number, total population and population density. The method we used is correlation coefficient analysis and linear regression.


```{r load required package}
library(leaflet)
library(dplyr)
library(rvest)
library(RJSONIO)
library(ggplot2)
library(data.table)
```

##Crawling data and Convert to data frame

```{r crawling data}
population <-"https://worldpopulationreview.com/countries/" %>%
  read_html() %>% html_nodes("table")%>% html_table(fill=TRUE)
pop<-population[[1]]

Coronavirus_Cases <-"https://www.worldometers.info/coronavirus/" %>%
  read_html() %>% html_nodes("table")%>% html_table(fill=TRUE)
Cor<-Coronavirus_Cases[[1]]
```

##Merge the two data set


```{r data merge}
#Modify the name of the data column in order to join the two data into one dataset
colnames(Cor)[1] <- 'Country'

#do some data cleaning to unify the country name in order to join the two data into one dataset

Cor$Country[which(Cor$Country=="S. Korea")]="South Korea"
pop$Country[which(pop$Country=="United Kingdom")]="UK"
pop$Country[which(pop$Country=="Czech Republic")]="Czechia"
pop$Country[which(pop$Country=="United Arab Emirates")]="UAE"
pop$Country[which(pop$Country=="Macedonia")]="North Macedonia"
pop$Country[which(pop$Country=="Reunion")]="R¨¦union"
pop$Country[which(pop$Country=="DR Congo")]="DRC"
pop$Country[which(pop$Country=="Faroe Islands")]="Faeroe Islands"
pop$Country[which(pop$Country=="Curacao")]="Cura¨¦ao"
pop$Country[which(pop$Country=="Cape Verde")]="Cabo Verde"
pop$Country[which(pop$Country=="Macau")]="Macao"
Cor$Country[which(Cor$Country=="CAR")]="Central African Republic"
Cor$Country[which(Cor$Country=="Turks and Caicos")]="Turks and Caicos Islands"
Cor$Country[which(Cor$Country=="St. Barth")]="Saint Barth¨¦lemy"
Cor$Country[which(Cor$Country=="Saint Pierre Miquelon")]="Saint Pierre and Miquelon"
Cor$Country[which(Cor$Country=="USA")]="United States"

#Left join population data and COVID-19 data


dataworld <- left_join(Cor, pop, by='Country')
```

##do some data cleaning

```{r data cleaning}
#keep only the not null Population for further analysis
dataworld<-dataworld%>%filter(!is.na(`2020 Population`))

#remove unwated columns of the dataworld

dataworld$`2019 Population`<-NULL

#Modify the name of the data column

colnames(dataworld)[8] <- 'SeriousCritical'

#Convert the data type in dataworld from char to num  

dataworld$TotalCases<-gsub(",", "", dataworld$TotalCases)
dataworld$TotalCases<-as.numeric(dataworld$TotalCases)
dataworld$`2020 Population`<-gsub(",", "", dataworld$`2020 Population`)
dataworld$`2020 Population`<-as.numeric(dataworld$`2020 Population`)
dataworld$TotalDeaths<-gsub(",", "", dataworld$TotalDeaths)
dataworld$TotalDeaths<-as.numeric(dataworld$TotalDeaths)  
dataworld$TotalRecovered<-gsub(",", "", dataworld$TotalRecovered)
dataworld$TotalRecovered<-as.numeric(dataworld$TotalRecovered)
dataworld$ActiveCases<-gsub(",", "", dataworld$ActiveCases)
dataworld$ActiveCases<-as.numeric(dataworld$ActiveCases)
dataworld$SeriousCritical<-gsub(",", "", dataworld$SeriousCritical)
dataworld$SeriousCritical<-as.numeric(dataworld$SeriousCritical)
dataworld$TotalTests<-gsub(",", "", dataworld$TotalTests)
dataworld$TotalTests<-as.numeric(dataworld$TotalTests)
dataworld$`Area (km2)`<-gsub(",","",dataworld$`Area (km2)`)
dataworld$`Area (km2)`<-as.numeric(dataworld$`Area (km2)`)

#Use the data in the dataworld table to calculate the mortality and morbidity of new coronavirus, and store them in the world table

world<-mutate(dataworld,Prevalence=dataworld$TotalCases/dataworld$`2020 Population`)
world<-mutate(world,Mortality=world$TotalDeaths/world$`2020 Population`)

#save the cleaned data into disk

write.csv(world,file = "world.csv",row.names = F)
world

knitr::kable(world)
```

## mortality and morbidity of  COVID-19 visulization

```{r mortality and morbidity of  COVID-19 visulization}
#map user location
world_data<-read.csv("world.csv",encoding="UTF-8")


#filter data with location


world_outbreak<-subset(world_data, Country!="")$Country


#clean geocode location


world_outbreak<-sapply(world_outbreak,function(row) iconv(row, "latin1", "ASCII", sub=""))


#Install key package helpers:


source("https://raw.githubusercontent.com/LucasPuente/geocoding/master/geocode_helpers.R")


#Install modified version of the geocode function(that now includes the api_key parameter):


source("https://raw.githubusercontent.com/LucasPuente/geocoding/master/modified_geocode.R")

#Generate specific geocode function:


geocode_apply<-function(x){
  geocode(x, source = "google", output = "all", api_key="AIzaSyAy96kx7Iw_h2dUSpoSP91Y5Cy7GVQC108")
}


#Apply this new function to entire list:


geocode_results<-sapply(world_outbreak, geocode_apply, simplify = F)


#Look at the number of geocoded locations:


length(geocode_results)


#Only keep locations with "status" = "ok"


condition_a <- sapply(geocode_results, function(x) x["status"]=="OK")
geocode_results<-geocode_results[condition_a]


#Only keep locations with one match:


condition_b <- lapply(geocode_results, lapply, length)
condition_b2<-sapply(condition_b, function(x) x["results"]=="1")
geocode_results<-geocode_results[condition_b2]


#Look at the number of *successfully* geocoded locations:


length(geocode_results)


#Address formatting issues:


source("https://raw.githubusercontent.com/LucasPuente/geocoding/master/cleaning_geocoded_results.R")


#Turn list into a data.frame:


results_b<-lapply(geocode_results, as.data.frame)
results_c<-lapply(results_b,function(x) subset(x, select=c("results.formatted_address", "results.geometry.location")))

#Format thes new data frames:

results_d<-lapply(results_c,function(x) data.frame(Location=x[1,"results.formatted_address"],
                                                   lat=x[1,"results.geometry.location"],
                                                   lng=x[2,"results.geometry.location"]))

#Bind these data frames together:

results_e<-rbindlist(results_d)

#Add info on the original (i.e. user-provided) locatio/'-n string:

results_f<-results_e[,Original_Location:=names(results_d)]

#Modify the name of the data column

colnames(world_data)[1] <- 'Location'

#Left join world_data table and result_f table to form dataworld table

result_r <- left_join(results_f, world_data, by='Location')

#Global mortality rates are shown on the map

site_locations <- leaflet(result_r) %>%
  addTiles() %>%
  addCircleMarkers(lng = ~lng, lat = ~lat, popup = ~result_r,
                   radius = ~sqrt(Mortality) * 260, stroke = FALSE, color = "red",opacity = 0.1,fillOpacity = 0.8)

site_locations


#Global Prevalence rates are shown on the map


site_locations1 <- leaflet(result_r) %>%
  addTiles() %>%
  addCircleMarkers(lng = ~lng, lat = ~lat, popup = ~result_r,
                   radius = ~sqrt(Prevalence) * 100, stroke = FALSE, color = "red",opacity = 0.1,fillOpacity = 0.8)

site_locations1
```

## analyze the relationship of total death with the other factors

From the scatter plot and the correlation coefficient, we can see that total death show strong correlation with Total infected Cases, TotalRecovered case, SeriousCritical case, ActiveCases. And total death show medium correlation with TotalTests. While weak relationsip with total population and population density.

```{r scatter plot and correlation coefficient}
p1<-ggplot(data=dataworld,aes(x=TotalCases,y=TotalDeaths,col=TotalCases))+guides(col=FALSE)+
  geom_point() +  theme_bw()  + 
  labs(x="TotalCases", y="TotalDeaths", 
       title="")
p1

p2<-ggplot(data=dataworld,aes(x=TotalRecovered,y=TotalDeaths,col=TotalRecovered))+guides(col=FALSE)+
  geom_point() +  theme_bw()  + 
  labs(x="TotalRecovered", y="TotalDeaths", 
       title="")
p2

p3<-ggplot(data=dataworld,aes(x=SeriousCritical,y=TotalDeaths,col=SeriousCritical))+guides(col=FALSE)+
  geom_point() +  theme_bw()  + 
  labs(x="SeriousCritical", y="TotalDeaths", 
       title="")
p3

p4<-ggplot(data=dataworld,aes(x=TotalTests,y=TotalDeaths,col=TotalTests))+guides(col=FALSE)+
  geom_point() +  theme_bw()  + 
  labs(x="TotalTests", y="TotalDeaths", 
       title="")
p4

p5<-ggplot(data=dataworld,aes(x=`2020 Population`,y=TotalDeaths,col=`2020 Population`))+guides(col=FALSE)+
  geom_point() +  theme_bw()  + 
  labs(x="2020 Population", y="TotalDeaths", 
       title="")
p5

## calculate the population density
dataworld<-mutate(dataworld,Population_density=dataworld$`2020 Population`/dataworld$`Area (km2)`)

p6<-ggplot(data=dataworld,aes(x=Population_density,y=TotalDeaths,col=Population_density))+guides(col=FALSE)+
  geom_point() +  theme_bw()  + 
  labs(x="Population_density", y="TotalDeaths", 
       title="")
p6



## calculate the correlation coefficient
test<-dataworld
test<-test%>%filter(!is.na(TotalDeaths))
test1<-test%>%filter(!is.na(TotalCases))
cor(test1$TotalCases,test1$TotalDeaths)

test2<-test%>%filter(!is.na(TotalRecovered))
cor(test2$TotalRecovered,test2$TotalDeaths)

test3<-test%>%filter(!is.na(SeriousCritical))
cor(test3$SeriousCritical,test3$TotalDeaths)

cor(test$ActiveCases,test$TotalDeaths)

test4<-test%>%filter(!is.na(TotalTests))
cor(test4$TotalTests,test4$TotalDeaths)

cor(test$TotalDeaths,test$`2020 Population`)

cor(test$TotalDeaths,test$Population_density)
```


## fit a linear model to learn the relationship of total death with the other factors

From the result of multiple linear regression model, we can see the whole regression model is significant with R square reach 1 and F test give significant result. From the coefficient, we can see TotalCases,TotalRecovered and ActiveCases is significant under significant level 0.05. We can see from the linear regression equation, TotalCases,SeriousCritical,2020 Population shows positive relation with total death. While TotalRecovered,ActiveCases, TotalTests, Population_density shows negative relationship with total death.

```{r linear regression model}
lmo<-lm(TotalDeaths~TotalCases+TotalRecovered+SeriousCritical+ActiveCases+TotalTests+`2020 Population`+Population_density,data=dataworld)
summary(lmo)
```


























